---
title: "Trends in KEEN Swath Data"
author: "Jarrett Byrnes"
date: "10/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
```

# What species are in the swath data?

```{r dat, echo = FALSE, warning = FALSE, message = FALSE}
library(dplyr)
library(readr)
library(purrr)
library(ggplot2)
library(glmmTMB)
library(broom.mixed)
library(tidyr)

swath <- read_csv("data/keen/keen_swath.csv") %>%
  tidyr::drop_na(SPECIES) %>%
  filter(is.na(SIZE) | SIZE == "<10cm") %>%
  filter(!(SP_CODE %in% c("CUFR", "CYLU",
                          "MYOC", "MYSC",
                          "ULSP", "TAAD"))) %>% #too few obs
  complete(YEAR, SITE, SP_CODE, 
           TRANSECT, SIDE, QUAD,
           fill = list(COUNT = 0)) %>% #because data is long
  group_by(SP_CODE) %>% #fix NAs creates
  mutate(SPECIES = na.omit(unique(SPECIES)),
         COMMON.NAME = na.omit(unique(COMMON.NAME))) %>%
  ungroup()

knitr::kable(swath %>%
               select(SP_CODE, COMMON.NAME, SPECIES) %>%
               group_by(SP_CODE, COMMON.NAME, SPECIES) %>% 
               slice(1L) %>% 
               ungroup(),
             "html") %>%
  kableExtra::kable_styling()
```

# Let's Plot Trends
Here are some functions we'll apply to each species. I'll then fit mixed models with all of them using   

<center>COUNT ~ YEAR * SITE + (1|TRANSECT)</center>

with a gaussian error. Note, it's count, so, I could use Poisson, but, that needs to be way more tuned to each model - this should be fine for a first cut?

Here's how we'll do it:

```{r, echo = TRUE}
tseries_plot <- function(adf){
  
  ggplot(adf,
         aes(y = COUNT, x = YEAR,
             color = TRANSECT)) +
    stat_summary(fun.data = mean_se) +
    stat_summary(fun.data = mean_se, geom = "line") +
    facet_wrap(~SITE, nrow = 2) +
    labs(color = "Transect", 
         y = "Count per 20 sq m ± SE",  x = "Year",
         title = adf$SPECIES[1])
}

tseries_fun <- function(adf){
  glmmTMB(COUNT ~ YEAR * SITE + (1|TRANSECT),
               data = adf,
               family = gaussian)
  
}

generate_output <- function(adf){
  cat(paste0("## ", adf$SPECIES[1], "  \n<br>"))
  
  tseries_plot(adf) %>% print()
  
  tseries_fun(adf) %>% 
    car::Anova(test.statistic  = "Chisq") %>% 
    tidy() %>%
    knitr::kable("html", digits = 2) %>% 
    kableExtra::kable_styling() %>%
    print
  
  cat("\n\n")
}
```

Now let's `purrr::walk()` through the whole shebang.

```{r, echo = TRUE, results = "asis", warning = FALSE}
walk(split(swath, swath$SP_CODE), generate_output)
```
