---
title: "Trends in KEEN Aggregate Data"
author: "Jarrett Byrnes"
date: "12/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = here::here())

# algal cover
# invert cover
# red cover
# total mobiles in swath
```

# Load and Aggregate the Data

```{r dat, echo = FALSE, warning = FALSE, message = FALSE, results = 'asis'}
library(dplyr)
library(readr)
library(purrr)
library(ggplot2)
library(broom)
library(lme4)
library(tidyr)

upc <- read_csv("data/keen/keen_cover.csv") %>%
  mutate(TRANSECT = gsub("^8 Ball", "Magic 8 Ball", TRANSECT)) %>%
  tidyr::drop_na(SPECIES) %>%
  tidyr::drop_na(SITE) %>%
  tidyr::drop_na(TRANSECT) %>%
  filter(TRANSECT != "NA") %>%
  filter(DIVISION.FAMILY != "Echinoderms") %>%
  filter(DIVISION.FAMILY != "Arthropods") %>%
  
  # filter(is.na(SIZE) | SIZE == "<10cm") %>%
  # filter(!(SP_CODE %in% c("CUFR", "CYLU",
  #                         "MYOC", "MYSC",
  #                         "ULSP", "TAAD"))) %>% #too few obs
  complete(YEAR, nesting(SITE, TRANSECT), SP_CODE,
           fill = list(PERCENT_COVER = 0)) %>% #because data is long
  group_by(SP_CODE) %>% #fix NAs creates
  mutate(SPECIES = na.omit(unique(SPECIES)),) %>%
  ungroup()

swath <- read_csv("data/keen/keen_swath.csv") %>%
  tidyr::drop_na(SPECIES) %>%
  filter(is.na(SIZE) | SIZE == "<10cm") %>%
  filter(!(SP_CODE %in% c("CUFR", "CYLU",
                          "MYOC", "MYSC",
                          "ULSP", "TAAD"))) %>% #too few obs
  complete(YEAR, nesting(SITE, 
           TRANSECT, SIDE, QUAD), SP_CODE,
           fill = list(COUNT = 0)) %>% #because data is long
  group_by(SP_CODE) %>% #fix NAs creates
  mutate(SPECIES = na.omit(unique(SPECIES)),
         COMMON.NAME = na.omit(unique(COMMON.NAME))) %>%
  ungroup()



fish <- read_csv("data/keen/keen_fish.csv") %>%
  tidyr::drop_na(SPECIES) %>%
  filter(FISH.SIZE != "YOY") %>%
  complete(YEAR, nesting(SITE, 
           TRANSECT, SIDE, QUAD, ), SP_CODE, 
           fill = list(COUNT = 0)) %>% #because data is long
  group_by(SP_CODE) %>% #fix NAs creates
  mutate(SPECIES = na.omit(unique(SPECIES)),
         COMMON.NAME = na.omit(unique(COMMON.NAME))) %>%
  ungroup()  %>%
  group_by(YEAR, SITE, TRANSECT) %>%
  summarize(COUNT = sum(COUNT, na.rm=T)) %>%
  ungroup()
```

```{r}
group_sum <- . %>%
  group_by(YEAR, SITE, TRANSECT) %>%
  summarize(PERCENT_COVER = sum(PERCENT_COVER, na.rm=T)) %>%
  ungroup()

algae <- upc %>%
  filter(GROUP == "Algae") %>%
  group_sum

inverts <-  upc %>%
  filter(GROUP == "Invertebrate") %>%
  group_sum

reds <- upc %>%
  filter(COMMON.DIVISION.NAME == "Erect Red Algae") %>%
  group_sum %>%
  filter(PERCENT_COVER != 0) #weird error


browns <- upc %>%
  filter(COMMON.DIVISION.NAME == "Brown Algae") %>%
  group_sum %>%
  filter(PERCENT_COVER != 0) #weird error


bryo <- upc %>%
  filter(COMMON.DIVISION.NAME == "Bryozoans") %>%
  group_sum 


squirts <- upc %>%
  filter(COMMON.DIVISION.NAME == "Tunicates") %>%
  group_sum 

crusts <- upc %>%
  filter(COMMON.DIVISION.NAME == "Red Algal Crusts") %>%
  group_sum

#ok, mobiles from swath
group_sum_swath <- . %>%
  group_by(YEAR, SITE, TRANSECT) %>%
  summarize(COUNT = sum(COUNT, na.rm=T)) %>%
  ungroup()

crustaceans <- swath %>%
  filter(COMMON.DIVISION.NAME == "Crustaceans") %>%
  group_sum_swath

stars <- swath %>%
  filter(COMMON.DIVISION.NAME == "Sea Stars") %>%
  group_sum_swath


#fish
```

# Let's Plot Trends
Here are some functions we'll apply to each species. I'll then fit mixed models with all of them using   

<center>COUNT ~ YEAR * SITE + (1|TRANSECT)</center>

with a gaussian error. Note, it's cover, so, I could use Beta, but, that needs to be way more tuned to each model given that we have > 100% cover for some things - this should be fine for a first cut?

Here's how we'll do it:

```{r, echo = TRUE}
tseries_plot <- function(adf){
  
  ggplot(adf,
         aes(y = PERCENT_COVER, x = YEAR,
             color = TRANSECT)) +
    geom_point() +
    geom_line() +
    facet_wrap(~SITE, nrow = 2) +
    labs(color = "Transect", 
         y = "Percent Cover",  x = "Year")
}

tseries_fun <- function(adf){
  lmer(PERCENT_COVER ~ YEAR * SITE + (1|TRANSECT),
               data = adf)
  
}

generate_output <- function(adf){
 # cat(paste0("## ", adf$SP_CODE[1], " ", adf$SPECIES[1], "  \n<br>"))
    cat("\n\n")

  tseries_plot(adf) %>% print()

  if(sum(adf$PERCENT_COVER>3) > 2){
  tseries_fun(adf) %>%
    car::Anova(test.statistic  = "Chisq") %>%
    tidy() %>%
    knitr::kable(digits = 3) %>%
 #   kableExtra::kable_styling() %>%
   print
  }
  
}
```


## All Algae Percent Cover
```{r}
generate_output(algae)
```

## All Browns Percent Cover
```{r}
generate_output(algae)
```

## All Reds Percent Cover
```{r}
generate_output(reds)
```

## All Browns Percent Cover
```{r}
generate_output(browns)
```


## All Inverts Percent Cover
```{r}
generate_output(inverts)
```

## All Bryozoans Percent Cover
```{r}
generate_output(bryo)
```


## All Tunicates Percent Cover
```{r}
generate_output(squirts)
```

## All Crusts Percent Cover
```{r}
generate_output(crusts)
```


```{r, echo = FALSE}
tseries_plot_swath <- function(adf){
  
  ggplot(adf,
         aes(y = COUNT, x = YEAR,
             color = TRANSECT)) +
    geom_point() +
    geom_line() +
    facet_wrap(~SITE, nrow = 2) +
    labs(color = "Transect", 
         y = "Count",  x = "Year")
}

tseries_fun_swath <- function(adf){
  lmer(COUNT ~ YEAR * SITE + (1|TRANSECT),
               data = adf)
  
}

generate_output_swath <- function(adf){
 # cat(paste0("## ", adf$SP_CODE[1], " ", adf$SPECIES[1], "  \n<br>"))
  cat("\n\n")

  tseries_plot_swath(adf) %>% print()

  if(sum(adf$COUNT>3) > 2){
  tseries_fun_swath(adf) %>%
    car::Anova(test.statistic  = "Chisq") %>%
    tidy() %>%
    knitr::kable(digits = 3) %>%
   # kableExtra::kable_styling() %>%
    print
  }
  
}
```

## All Crustaceans Count
```{r}
generate_output_swath(crustaceans)
```

## All Stars Count
```{r}
generate_output_swath(stars)
```


## All Fish Count
```{r}
generate_output_swath(fish)
```
