---
title: "Trends in SML intertidal data (sessile species)"
author: "Kylla Benes"
date: "12/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
```

## What species are in the rocky intertidal data?


```{r dat, echo = FALSE, warning = FALSE, message = FALSE}
library(dplyr)
library(readr)
library(purrr)
library(ggplot2)
library(glmmTMB)
library(broom.mixed)
library(tidyr)

data <- read.csv("data/intertidal/percent_cover_data.csv")
data2 <-  filter(data, Percent_cover != "p", Percent_cover != "nd", Percent_cover != "upper 15.6%/substrate 1.2%", Percent_cover != "if a species is not listed to the left, please put it in the notes") #this is not working, "Error in match.arg(method) : object 'Percent_cover' not found"
data$Transect<-factor(data$Transect)
data$Percent_cover<-as.numeric(as.character(data$Percent_cover)) #text turned to NAs
data$Organism<-factor(data$Organism)
```

# Let's Plot Trends
Here are some functions we'll apply to each species. I'll then fit mixed models with all of them using   

<center>COVER ~ YEAR + (1|TRANSECT)</center>

with a gaussian error. Note, it's count, so, I could use Poisson, but, that needs to be way more tuned to each model - this should be fine for a first cut?

Here's how we'll do it:
```{r}
tseries_plot <- function(data){
  
  ggplot(data,
         aes(y = Percent_cover, x = Year,
             color = Transect)) +
    stat_summary(fun.data = mean_se) +
    stat_summary(fun.data = mean_se, geom = "line") +
    labs(color = "Transect", 
         y = "Percent Cover ± SE",  x = "Year")
}

tseries_fun <- function(data){
  glmmTMB(Percent_cover ~ Year + (1|Transect),
               data = data,
               family = gaussian)
  
}

generate_output <- function(data){
  cat(paste0("## ", data$Organism[1], " ", data$Organism[1], "  \n<br>"))
  
  tseries_plot(data) %>% print()
  
  # tseries_fun(adf) %>% 
  #   car::Anova(test.statistic  = "Chisq") %>% 
  #   tidy() %>%
  #   knitr::kable("html", digits = 3) %>% 
  #   kableExtra::kable_styling() %>%
  #   print
  # 
  cat("\n\n")
}
```
Now let's `purrr::walk()` through the whole shebang.

```{r, echo = TRUE, results = "asis", warning = FALSE}
walk(split(data, data$Organism), generate_output)
```
