---
title: "Trends in SML Aggregate Data"
author: "Kylla Benes (adapted from: Jarrett Byrnes)"
date: "3/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = here::here())

# algal cover
# invert cover
# red cover
# total mobiles in swath
```

# Load and Aggregate the Data

```{r dat, echo = FALSE, warning = FALSE, message = FALSE, results = 'asis'}
library(dplyr)
library(readr)
library(purrr)
library(ggplot2)
library(broom)
library(lme4)
library(tidyr)

pc = read.csv("data/intertidal/pc_clean.csv", header=TRUE, 
                   na.strings = c("NA"))

ct = read.csv("data/intertidal/ct_clean.csv", header=TRUE, 
              na.strings = c("NA"))

# Combine df-------------------
pc_agg <- pc %>%
  mutate(type = case_when(Organism == "Ascophyllum nodosum (canopy)" ~ "Algae",
                          Organism == "Ascophyllum nodosum (primary)" ~ "Algae",
                          Organism == "Acoela" ~ "Invertebrate",
                          Organism == "Acrosiphonia" ~ "Algae",
                          Organism == "Ahnfeltia plicata" ~ "Algae",
                          Organism == "Alaria esculenta" ~ "Algae",
                          Organism == "Alaria esculenta (canopy)" ~ "Algae",
                          Organism == "Alaria esculenta (primary)" ~ "Algae",
                          Organism == "Alcyonidium" ~ "Invertebrate",
                          Organism == "Amathia" ~ "Invertebrate",
                          Organism == "Amphipoda" ~ "Invertebrate",
                          Organism == "Anomia simplex" ~ "Invertebrate",
                          Organism == "Antithamnion" ~ "Algae",
                          Organism == "Anurida maritima" ~ "Invertebrate",
                          Organism == "Aplidium" ~ "Invertebrate",
                          Organism == "Arthopyrenia" ~ "Fungi",
                          Organism == "Ascophyllum nodosum" ~ "Algae",
                          Organism == "Asterias forbesi" ~ "Invertebrate",
                          Organism == "Asterias rubens" ~ "Invertebrate",
                          Organism == "Astyris lunata" ~ "Invertebrate",
                          Organism == "Audouinella"~ "Algae",
                          Organism == "Bangia atropurpurea" ~ "Algae",
                          Organism == "Black zone"~"Algae",
                          Organism == "Bonnemaisonia hamifera" ~ "Algae",
                          Organism == "Bonnemaisonia hamifera (Trailiella phase)" ~ "Algae",
                          Organism == "Boreochiton ruber" ~ "Invertebrate",
                          Organism == "Botrylloides aureum"~ "Invertebrate",
                          Organism == "Botrylloides violaceus" ~ "Invertebrate",
                          Organism == "Botryllus schlosseri" ~ "Invertebrate",
                          Organism == "Bugula neritina" ~ "Invertebrate",
                          Organism == "Callophyllis" ~ "Algae",
                          Organism == "Callopora" ~ "Invertebrate",
                          Organism == "Cancer borealis" ~ "Invertebrate",
                          Organism == "Cancer irroratus" ~ "Invertebrate",
                          Organism == "Cancer" ~ "Invertebrate",
                          Organism == "Celleporella hyalina" ~ "Invertebrate",
                          Organism == "Ceramium virgatum" ~ "Algae",
                          Organism == "Ceramium virgatum (canopy)" ~ "Algae",
                          Organism == "Ceramium virgatum (primary)" ~ "Algae",
                          Organism == "Cerianthus" ~ "Invertebrate",
                          Organism == "Chaetomorpha" ~ "Algae",
                          Organism == "Chlorella" ~ "Algae",
                          Organism == "Chondrus crispus" ~ "Algae",
                          Organism == "Chondrus crispus (canopy)" ~ "Algae",
                          Organism == "Chondrus crispus (primary)" ~ "Algae",
                          Organism == "Chorda filum" ~ "Algae",
                          Organism == "Chordaria flagelliformis" ~ "Algae",
                          Organism == "Cirratulus" ~ "Invertebrate",
                          Organism == "Cladophora rupestris" ~ "Algae",
                          Organism == "Cladophora" ~ "Algae",
                          Organism == "Cladostephus spongiosus" ~ "Algae",
                          Organism == "Clathromorphum circumscriptum" ~ "Algae",
                          Organism == "Codium fragile" ~ "Algae",
                          Organism == "Codium fragile (canopy)" ~ "Algae",
                          Organism == "Codium fragile (primary)" ~ "Algae",
                          Organism == "Colpomenia peregrina" ~ "Algae",
                          Organism == "Colus stimpsoni" ~ "Invertebrate",
                          Organism == "Corallina officinalis" ~ "Algae",
                          Organism == "Coralline (crust)" ~ "Algae",
                          Organism == "Coryphella" ~ "Invertebrate",
                          Organism == "Crepidula fornicata" ~ "Invertebrate",
                          Organism == "Cribrilina" ~ "Invertebrate",
                          Organism == "Cryptosula pallasiana" ~ "Invertebrate",
                          Organism == "Culicoides" ~ "Invertebrate",
                          Organism == "Cyanobacteria" ~ "Algae",
                          Organism == "Cystoclonium purpureum" ~ "Algae",
                          Organism == "Dendrodoa" ~ "Invertebrate",
                          Organism == "Dendronotus"~"Invertebrate",
                          Organism == "Devaleraea ramentacea"~"Algae",
                          Organism == "Diadumene lineata"~"Invertebrate",
                          Organism == "Didemnum vexillum"~"Invertebrate",
                          Organism == "Diplosoma"~"Invertebrate",
                          Organism == "Dynamena pumila"~"Invertebrate",
                          Organism == "Ectocarpus"~"Algae",
                          Organism == "Ectopleura crocea"~"Invertebrate",
                          Organism == "Elachista fucicola"~"Algae",
                          Organism == "Electra pilosa"~"Invertebrate",
                          Organism == "Erythrotrichia carnea"~"Algae",
                          Organism == "Euplana"~"Invertebrate",
                          Organism == "Euthora cristata"~"Algae",
                          Organism == "Fabricia"~"Invertebrate",
                          Organism == "Flustrellidra hispida"~"Invertebrate",
                          Organism == "Foviella"~"Invertebrate",
                          Organism == "Fucus distichus"~"Algae",
                          Organism == "Fucus distichus (canopy)"~"Algae",
                          Organism == "Fucus distichus (primary)"~"Algae",
                          Organism == "Fucus spiralis"~"Algae",
                          Organism == "Fucus spiralis (canopy)"~"Algae",
                          Organism == "Fucus spiralis (primary)"~"Algae",
                          Organism == "Fucus vesiculosus"~"Algae",
                          Organism == "Fucus vesiculosus (canopy)"~"Algae",
                          Organism == "Fucus vesiculosus (canopy)"~"Algae",
                          Organism == "Fucus"~"Algae",
                          Organism == "Fucus (canopy)"~"Algae",
                          Organism == "Fucus (primary)"~"Algae",
                          Organism == "Halacarus"~"Invertebrate",
                          Organism == "Halichondria"~"Invertebrate",
                          Organism == "Hemigrapsus sanguineus"~"Invertebrate",
                          Organism == "Henricia sanguinolenta"~"Invertebrate",
                          Organism == "Hiatella arctica"~"Invertebrate",
                          Organism == "Hildenbrandia rubra"~"Algae",
                          Organism == "Hincksia granulosa"~"Algae",
                          Organism == "Idotea balthica"~"Invertebrate",
                          Organism == "Idotea balthica"~"Invertebrate",
                          Organism == "Lacuna vincta"~"Invertebrate",
                          Organism == "Leathesia marina"~"Algae",
                          Organism == "Lepidonotus"~"Invertebrate",
                          Organism == "Leucosolenia"~"Invertebrate",
                          Organism == "Lithophyllum"~"Algae",
                          Organism == "Littorina littorea"~"Invertebrate",
                          Organism == "Littorina obtusata"~"Invertebrate",
                          Organism == "Littorina saxatilis"~"Invertebrate",
                          Organism == "Mastocarpus stellatus"~"Algae",
                          Organism == "Mastocarpus stellatus (canopy)"~"Algae",
                          Organism == "Mastocarpus stellatus (primary)"~"Algae",
                          Organism == "Mastocarpus stellatus (crust)"~"Algae",
                          Organism == "Membranipora membranacea"~"Invertebrate",
                          Organism == "Metridium senile"~"Invertebrate",
                          Organism == "Microporella ciliata"~"Invertebrate",
                          Organism == "Micrura affinis"~"Invertebrate",
                          Organism == "Modiolus modiolus"~"Invertebrate",
                          Organism == "Molgula"~"Invertebrate",
                          Organism == "Monostroma"~"Algae",
                          Organism == "Mya arenaria"~"Invertebrate",
                          Organism == "Mytilus edulis"~"Invertebrate",
                          Organism == "Namanereis"~"Invertebrate",
                          Organism == "Nicolea"~"Invertebrate",
                          Organism == "Notoplana"~"Invertebrate",
                          Organism == "Nucella lapillus"~"Invertebrate",
                          Organism == "Nudibranchia"~"Invertebrate",
                          Organism == "Onchidoris"~"Invertebrate",
                          Organism == "Ophiopholis"~"Invertebrate",
                          Organism == "Ostrea edulis"~"Invertebrate",
                          Organism == "Pagurus acadianus"~"Invertebrate",
                          Organism == "Palmaria palmata"~"Algae",
                          Organism == "Petalonia fascia"~"Algae",
                          Organism == "Phymatolithon lenormandii"~"Algae",
                          Organism == "Platyhelminthes"~"Invertebrate",
                          Organism == "Platyhelminthes"~"Invertebrate",
                          Organism == "Plumaria plumosa"~"Algae",
                          Organism == "Polychaeta"~"Invertebrate",
                          Organism == "Polysiphonia"~"Algae",
                          Organism == "Polysiphonia (canopy)"~"Algae",
                          Organism == "Polysiphonia (primary)"~"Algae",
                          Organism == "Porphyra"~"Algae",
                          Organism == "Prasiola stipitata"~"Algae",
                          Organism == "Praunus"~"Invertebrate",
                          Organism == "Protectocarpus speciosus"~"Algae",
                          Organism == "Pterothamnion plumula"~"Algae",
                          Organism == "Ptilota serrata"~"Algae",
                          Organism == "Pylaiella littoralis"~"Algae",
                          Organism == "Ralfsia"~"Algae",
                          Organism == "Rhizoclonium tortuosum"~"Algae",
                          Organism == "Saccharina latissima"~"Algae",
                          Organism == "Saccharina latissima (canopy)"~"Algae",
                          Organism == "Saccharina latissima (primary)"~"Algae",
                          Organism == "Saccorhiza dermatodea"~"Algae",
                          Organism == "Schizoporella unicornis"~"Invertebrate",
                          Organism == "Scytosiphon lomentaria"~"Algae",
                          Organism == "Semibalanus balanoides"~"Invertebrate",
                          Organism == "Sertularia"~"Invertebrate",
                          Organism == "Skeneopsis planorbis"~"Invertebrate",
                          Organism == "Spermothamnion repens"~"Algae",
                          Organism == "Sphacelaria cirrosa"~"Algae",
                          Organism == "Sphacelaria"~"Algae",
                          Organism == "Spirorbis"~"Invertebrate",
                          Organism == "Spongomorpha aeruginosa"~"Algae",
                          Organism == "Strongylocentrotus droebachiensis"~"Invertebrate",
                          Organism == "Testudinalia testudinalis"~"Invertebrate",
                          Organism == "Thelepus cincinnatus"~"Invertebrate",
                          Organism == "Tricellaria"~"Invertebrate",
                          Organism == "Ulva intestinalis"~"Algae",
                          Organism == "Ulva lactuca"~"Algae",
                          Organism == "Verrucaria"~"Fungi",
                          Organism == "Vertebrata lanosa"~"Algae"
))



pc_agg <- pc_agg %>%
  mutate(subtype = case_when(
Organism == "Acrosiphonia"~"Green Algae",
Organism == "Ahnfeltia plicata"~"Erect Red Algae",
Organism == "Alaria esculenta"~"Erect Brown Algae",
Organism == "Alaria esculenta (canopy)"~"Erect Brown Algae",
Organism == "Alaria esculenta (primary)"~"Erect Brown Algae",
Organism == "Alcyonidium"~"Bryozoan",
Organism == "Amathia"~"Bryozoan",
Organism == "Amphipoda"~"Crustacean",
Organism == "Anomia simplex"~"Bivalve",
Organism == "Antithamnion"~"Erect Red Algae",
Organism == "Anurida maritima"~"Collembola",
Organism == "Aplidium"~"Tunicate",
Organism == "Arthopyrenia"~"Fungi",
Organism == "Ascophyllum nodosum"~"Erect Brown Algae",
Organism == "Ascophyllum nodosum (canopy)"~"Erect Brown Algae",
Organism == "Ascophyllum nodosum (primary)"~"Erect Brown Algae",
Organism == "Asterias forbesi"~"Sea Star",
Organism == "Asterias rubens"~"Sea Star",
Organism == "Astyris lunata"~"Gastropod",
Organism == "Audouinella"~"Erect Red Algae",
Organism == "Bangia atropurpurea"~"Erect Red Algae",
Organism == "Black zone"~"Cyanobacteria",
Organism == "Bonnemaisonia hamifera"~"Erect Red Algae",
Organism == "Bonnemaisonia hamifera (Trailiella phase)"~"Erect Red Algae",
Organism == "Boreochiton ruber"~"Polyplacophora",
Organism == "Botrylloides aureum"~"Tunicate",
Organism == "Botrylloides violaceus"~"Tunicate",
Organism == "Botryllus schlosseri"~"Tunicate",
Organism == "Bugula neritina"~"Bryozoan",
Organism == "Callophyllis"~"Erect Red Algae",
Organism == "Callopora"~"Bryozoan",
Organism == "Cancer"~"Crustacean",
Organism == "Cancer borealis"~"Crustacean",
Organism == "Cancer irroratus"~"Crustacean",
Organism == "Celleporella hyalina"~"Bryozoan",
Organism == "Ceramium virgatum"~"Erect Red Algae",
Organism == "Ceramium virgatum (canopy)"~"Erect Red Algae",
Organism == "Ceramium virgatum (primary)"~"Erect Red Algae",
Organism == "Cerianthus"~"Anthozoan",
Organism == "Chaetomorpha"~"Green Algae",
Organism == "Chlorella"~"Green Algae",
Organism == "Chondrus crispus"~"Erect Red Algae",
Organism == "Chondrus crispus (canopy)"~"Erect Red Algae",
Organism == "Chondrus crispus (primary)"~"Erect Red Algae",
Organism == "Chorda filum"~"Erect Brown Algae",
Organism == "Chordaria flagelliformis"~"Erect Brown Algae",
Organism == "Cirratulus"~"Worm",
Organism == "Cladophora"~"Green Algae",
Organism == "Cladophora rupestris"~"Green Algae",
Organism == "Cladostephus spongiosus"~"Erect Brown Algae",
Organism == "Clathromorphum circumscriptum"~"Red Algal Crust",
Organism == "Codium fragile"~"Green Algae",
Organism == "Codium fragile (canopy)"~"Green Algae",
Organism == "Codium fragile (primary)"~"Green Algae",
Organism == "Colpomenia peregrina"~"Erect Brown Algae",
Organism == "Colus stimpsoni"~"Gastropod",
Organism == "Corallina officinalis"~"Erect Red Algae",
Organism == "Coralline (crust)" ~"Red Algal Crust",
Organism == "Coryphella"~"Gastropod",
Organism == "Crepidula fornicata"~"Gastropod",
Organism == "Cribrilina"~"Bryozoan",
Organism == "Cryptosula pallasiana"~"Bryozoan",
Organism == "Culicoides"~"Crustacean",
Organism == "Cyanobacteria" ~ "Cyanobacteria",
Organism == "Cystoclonium purpureum"~"Erect Red Algae",
Organism == "Dendrodoa"~"Tunicate",
Organism == "Dendronotus"~"Gastropod",
Organism == "Devaleraea ramentacea"~"Erect Red Algae",
Organism == "Diadumene lineata"~"Anthozoan",
Organism == "Didemnum vexillum"~"Tunicate",
Organism == "Diplosoma"~"Tunicate",
Organism == "Dynamena pumila"~"Hydrozoan",
Organism == "Ectocarpus"~"Erect Brown Algae",
Organism == "Ectopleura crocea"~"Hydrozoan",
Organism == "Elachista fucicola"~"Erect Brown Algae",
Organism == "Electra pilosa"~"Bryozoan",
Organism == "Erythrotrichia carnea"~"Erect Red Algae",
Organism == "Euplana"~"Worm",
Organism == "Euthora cristata"~"Erect Red Algae",
Organism == "Fabricia"~"Worm",
Organism == "Flustrellidra hispida"~"Bryozoan",
Organism == "Foviella"~"Worm",
Organism == "Fucus"~"Erect Brown Algae",
Organism == "Fucus (canopy)"~"Erect Brown Algae",
Organism == "Fucus (primary)"~"Erect Brown Algae",
Organism == "Fucus distichus"~"Erect Brown Algae",
Organism == "Fucus distichus (canopy)"~"Erect Brown Algae",
Organism == "Fucus distichus (primary)"~"Erect Brown Algae",
Organism == "Fucus spiralis"~"Erect Brown Algae",
Organism == "Fucus spiralis (canopy)"~"Erect Brown Algae",
Organism == "Fucus spiralis (primary)"~"Erect Brown Algae",
Organism == "Fucus vesiculosus"~"Erect Brown Algae",
Organism == "Fucus vesiculosus (canopy)"~"Erect Brown Algae",
Organism == "Fucus vesiculosus (primary)"~"Erect Brown Algae",
Organism == "Halacarus"~"Crustacean",
Organism == "Halichondria"~"Sponge",
Organism == "Hemigrapsus sanguineus"~"Crustacean",
Organism == "Henricia sanguinolenta"~"Sea Star",
Organism == "Hiatella arctica"~"Bivalve",
Organism == "Hildenbrandia rubra"~"Red Algal Crust",
Organism == "Hincksia granulosa"~"Erect Brown Algae",
Organism == "Idotea balthica"~"Crustacean",
Organism == "Idotea balthica"~"Crustacean",
Organism == "Lacuna vincta"~"Gastropod",
Organism == "Leathesia marina"~"Erect Brown Algae",
Organism == "Lepidonotus"~"Worm",
Organism == "Leucosolenia"~"Sponge",
Organism == "Lithophyllum"~"Red Algal Crust",
Organism == "Littorina littorea"~"Gastropod",
Organism == "Littorina obtusata"~"Gastropod",
Organism == "Littorina saxatilis"~"Gastropod",
Organism == "Mastocarpus stellatus"~"Erect Red Algae",
Organism == "Mastocarpus stellatus (canopy)"~"Erect Red Algae",
Organism == "Mastocarpus stellatus (primary)"~"Erect Red Algae",
Organism == "Mastocarpus stellatus (crust)"~"Red Algal Crust",
Organism == "Membranipora membranacea"~"Bryozoan",
Organism == "Metridium senile"~"Anthozoan",
Organism == "Microporella ciliata"~"Bryozoan",
Organism == "Micrura affinis"~"Worm",
Organism == "Modiolus modiolus"~"Bivalve",
Organism == "Molgula"~"Tunicate",
Organism == "Monostroma"~"Green Algae",
Organism == "Mya arenaria"~"Bivalve",
Organism == "Mytilus edulis"~"Bivalve",
Organism == "Namanereis"~"Worm",
Organism == "Nicolea"~"Worm",
Organism == "Notoplana"~"Worm",
Organism == "Nucella lapillus"~"Gastropod",
Organism == "Nudibranchia"~"Gastropod",
Organism == "Onchidoris"~"Gastropod",
Organism == "Ophiopholis"~"Sea Star",
Organism == "Ostrea edulis"~"Bivalve",
Organism == "Pagurus acadianus"~"Crustacean",
Organism == "Palmaria palmata"~"Erect Red Algae",
Organism == "Petalonia fascia"~"Erect Brown Algae",
Organism == "Phymatolithon lenormandii"~"Red Algal Crust",
Organism == "Platyhelminthes"~"Worm",
Organism == "Platyhelminthes"~"Worm",
Organism == "Plumaria plumosa"~"Erect Red Algae",
Organism == "Polychaeta"~"Worm",
Organism == "Polysiphonia"~"Erect Red Algae",
Organism == "Polysiphonia (canopy)"~"Erect Red Algae",
Organism == "Polysiphonia (primary)"~"Erect Red Algae",
Organism == "Porphyra"~"Erect Red Algae",
Organism == "Prasiola stipitata"~"Green Algae",
Organism == "Praunus"~"Crustacean",
Organism == "Protectocarpus speciosus"~"Erect Brown Algae",
Organism == "Pterothamnion plumula"~"Erect Red Algae",
Organism == "Ptilota serrata"~"Erect Red Algae",
Organism == "Pylaiella littoralis"~"Erect Brown Algae",
Organism == "Ralfsia"~"Brown Algal Crust",
Organism == "Rhizoclonium tortuosum"~"Green Algae",
Organism == "Saccharina latissima"~"Erect Brown Algae",
Organism == "Saccharina latissima (canopy)"~"Erect Brown Algae",
Organism == "Saccharina latissima (primary)"~"Erect Brown Algae",
Organism == "Saccorhiza dermatodea"~"Erect Brown Algae",
Organism == "Schizoporella unicornis"~"Bryozoan",
Organism == "Scytosiphon lomentaria"~"Erect Brown Algae",
Organism == "Semibalanus balanoides"~"Crustacean",
Organism == "Sertularia"~"Hydrozoan",
Organism == "Skeneopsis planorbis"~"Gastropod",
Organism == "Spermothamnion repens"~"Erect Red Algae",
Organism == "Sphacelaria"~"Erect Brown Algae",
Organism == "Sphacelaria cirrosa"~"Erect Brown Algae",
Organism == "Spirorbis"~"Worm",
Organism == "Spongomorpha aeruginosa"~"Green Algae",
Organism == "Strongylocentrotus droebachiensis"~"Urchin",
Organism == "Testudinalia testudinalis"~"Gastropod",
Organism == "Thelepus cincinnatus"~"Worm",
Organism == "Tricellaria"~"Bryozoan",
Organism == "Ulva intestinalis"~"Green Algae",
Organism == "Ulva lactuca"~"Green Algae",
Organism == "Verrucaria"~"Fungi",
Organism == "Vertebrata lanosa"~"Erect Red Algae"))

pc_1986 <- pc_agg %>%
  filter(!is.na(Percent_cover)) %>%
  filter(Level<=13 & Level>=0) %>% 
  filter(between(Year, 1986, 2006))

pc_2009 <- pc_agg %>%
  filter(!is.na(Percent_cover)) %>%
  filter(Level<=13 & Level>=0) %>% 
  filter(between(Year, 2009, 2018))

pc_full=full_join(pc_1986, pc_2009)

pc_full$Transect<-factor(pc_full$Transect)
pc_full$Percent_cover<-as.numeric(as.character(pc_full$Percent_cover)) #text turned to NAs
pc_full$Organism<-factor(pc_full$Organism)
```

```{r}

#first sum up groups w/in plot
#then average across transect and exposure

group_type <- pc_full %>%
  group_by(Year, Transect, Level, Replicate, Exposure, type) %>%
  summarise(
    pc=sum(Percent_cover))

group_avg_type <- . %>%
  group_by(Year, Transect, Exposure) %>%
  summarize(pc = mean(pc, na.rm=T)) %>%
  ungroup()


algae <- group_type %>%
  filter(type == "Algae") %>%
  group_avg_type

inverts <-  group_type %>%
  filter(type == "Invertebrate") %>%
  group_avg_type


group_subtype <- pc_full %>%
  group_by(Year, Transect, Level, Replicate, Exposure, subtype) %>%
  summarise(
    pc=sum(Percent_cover))

group_avg_subtype <- . %>%
  group_by(Year, Transect, Exposure) %>%
  summarize(pc = mean(pc, na.rm=T)) %>%
  ungroup()

reds <- group_subtype %>%
  filter(subtype == "Erect Red Algae") %>%
  group_avg_subtype 

browns <- group_subtype %>%
  filter(subtype == "Erect Brown Algae") %>%
  group_avg_subtype 

greens <- group_subtype %>%
  filter(subtype == "Green Algae") %>%
  group_avg_subtype

red_crusts <- group_subtype %>%
  filter(subtype == "Red Algal Crust") %>%
  group_avg_subtype

brown_crusts <- group_subtype %>%
  filter(subtype == "Brown Algal Crust") %>%
  group_avg_subtype

cyan <- group_subtype %>%
  filter(subtype == "Cyanobacteria") %>%
  group_avg_subtype

bryo <- group_subtype %>%
  filter(subtype == "Bryozoan") %>%
  group_avg_subtype 

squirts <- group_subtype %>%
  filter(subtype == "Tunicate") %>%
  group_avg_subtype 

crustaceans <- group_subtype %>%
  filter(subtype == "Crustacean") %>%
  group_avg_subtype

bivalves <- group_subtype %>%
  filter(subtype == "Bivalve") %>%
  group_avg_subtype
```

# Let's Plot Trends
Here are some functions we'll apply to each species. I'll then fit mixed models with all of them using   

<center>COUNT ~ YEAR * EXPOSURE + (1|TRANSECT)</center>

with a gaussian error. Note, it's cover, so, I could use Beta, but, that needs to be way more tuned to each model given that we have > 100% cover for some things - this should be fine for a first cut?

Here's how we'll do it:

```{r, echo = TRUE}
tseries_plot <- function(adf){
  
  ggplot(adf,
         aes(y = pc, x = Year,
             color = Transect)) +
    geom_point() +
    geom_line() +
    facet_wrap(~Exposure, nrow = 1) +
    labs(color = "Transect", 
         y = "Percent Cover",  x = "Year")
}

tseries_fun <- function(adf){
  lmer(pc ~ Year * Exposure + (1|Transect),
               data = adf)
  
}

generate_output <- function(adf){
 # cat(paste0("## ", adf$SP_CODE[1], " ", adf$SPECIES[1], "  \n<br>"))
    cat("\n\n")

  tseries_plot(adf) %>% print()

  if(sum(adf$pc>3) > 2){
  tseries_fun(adf) %>%
    car::Anova(test.statistic  = "Chisq") %>%
    tidy() %>%
    knitr::kable(digits = 3) %>%
 #   kableExtra::kable_styling() %>%
   print
  }
  
}
```


## All Algae Percent Cover
```{r}
generate_output(algae)
```

## All Reds Percent Cover
```{r}
generate_output(reds)
```

## All Browns Percent Cover
```{r}
generate_output(browns)
```

## All Greens Percent Cover
```{r}
generate_output(greens)
```


## Red Crusts Percent Cover
```{r}
generate_output(red_crusts)
```


## Brown Crusts Percent Cover
```{r}
generate_output(brown_crusts)
```


## Cyanobacteria Percent Cover
```{r}
generate_output(cyan)
```


## All Inverts Percent Cover
```{r}
generate_output(inverts)
```

## All Bryozoans Percent Cover
```{r}
generate_output(bryo)
```


## All Tunicates Percent Cover
```{r}
generate_output(squirts)
```


## All Crustaceans Percent Cover
```{r}
generate_output(crustaceans)
```


## All Bivalves Percent Cover
```{r}
generate_output(bivalves)
```

